Constraint Grammar as a SAT problem

### 2015-05-22 paper/nodalida2015.tex
text about applications

\section{Results and evaluation}

\paragraph{Time}

>>>>

\section{Applications}

As described in Section~\ref{sec:eval}, our implementation is not
competetive with the state of the art. It is more fruitful to focus on
things where the SAT-based representation can make an impact.
One such thing is grammar analysis.

Traditionally, CG rules are applied deterministically and
sequentially; at the execution of rule, there is no way to
go back to earlier rules and undo them. Thus there is no way to know
what part of the input comes from the morphological analyser and what
from the CG.

A conflict can be defined as 
a set of two or more rules, such that applying the first makes the
next rules impossible to apply, regardless of input.
As a simple example, these rules could be

\begin{itemize}
\item [] \texttt{SELECT verb ;} \\
         \texttt{REMOVE verb IF (-1 det) ;}
\end{itemize}

The first rule selects the verb always, removing all other readings,
and the second rule removes verb reading, given certain condition.
If the rules are introduced in a different order, there is no
conflict: the REMOVE rule would not remove verb readings from all
possible verb analyses, so there is a possibility for the SELECT rule
to fire.

The way we implement SAT-CG is ideal for this kind of grammar
analysis. After applying each rule, it stores the clauses produced by
it and commits to them -- this makes the execution slow, but it
retains the dependencies.
Given the design that each rule application (instead of rule) gets a variable,
in case of a conflict, the program prints out the particular
application that violates the previous clauses, with the sentence
where it is applied. 
This conflict solving can be done per section, or for the whole grammar. 
In case of section-based, we run each section on the input, and give
the output as an input to the new section, discarding all clauses.

Maximisation-based conflict solving (conflicting rule set --> remove least
possible amount to get a non-conflicting rule set) is not feasible for this task. 
The whole definition of conflicts depends on ordering, and it would
not differentiate between the case where \texttt{SELECT verb} comes
before \texttt{REMOVE verb IF (-1 det)} or after.
On the other hand, a formalism such as FSIG would benefit from the
maximisation-based technique in conflict handling.

% SELECT (a) IF (0 PALJON + Nom + Sg) (1 N + Nom + Sg) ; # PALJO VALITTAMINEN
% SELECT (a) IF (0 PALJON + Par) (1 N + Par + Sg) ;
% SELECT (a) IF (0 PALJON + LOC-CASE) (1 N + 1 LOC-CASE + Sg) ;
% REMOVE (a) IF (0 PALJON) ; # "on asetettu paljon haltijaksi"

\section{Results and evaluation}
\label{sec:eval}
\paragraph{Time}
